formula1

### 2020-06-06 inst/f1points.Rmd
more commentary

From the above, we see that the first four drivers (Hamilton, Vettel,
Raikkonen, Bottas) are respectively first, second, third and fourth
according to both ranking procedures.  The lower-ranked players,
having estimated strengths of less than 0.03, are more scattered as
one might expect.

>>>>

From the above, we see that the first two drivers (Hamilton, Vettel)
are are respectively first and second according to both ranking
ranking procedures; but Raikkonen and Bottas are third and fourth, and
fourth and third, according to points and likelihood respectively.
The degree of agreement between the two systems might be quantified as
"two", for the positions of the top two drivers agree.
